The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-06-02 paper.tex
CMB foregrounds in introduction
lots of talking about CMB and its foregrounds, this will eventually be
an analogy to 21 cm foregrounds

Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
interstellar medium (ISM). Careful measurement and removal of contaminating foreground emission is
therefore an important component for CMB analysis \citep{2016A&A...594A..25P}. On large angular
scales galactic synchrotron, free-free, thermal dust, and anomolous microwave emission contribute.
On smaller angular scales point sources such as distant galaxies and quasars contribute
\citep{2016arXiv160603606D}.

Propagation effects from the IGM and intervening galaxy clusters can distort the thermal spectrum of
the CMB and impart information about the intervening material in those distortions. For instance the
measured optical depth to Thomson scattering implies a mean redshift of the Epoch of Reionization
(EoR) of ??? \todo{put number and citation}. The thermal Sunyaev--Zel'dovich effect does something
\todo{thing and citation}. The kinetic Synyaev--Zel'dovich effect does another thing \todo{thing and
citation}.

At redshifts $20 \gtrsim z \gtrsim 7$ neutral hydrogen is observable as a 10 to 100 mK perturbation
of the CMB spectrum due to the 21 cm hyperfine structure line of neutral hydrogen
\citep{2006PhR...433..181F, 2012RPPh...75h6901P}.  The spatial power spectrum of this perturbation
is expected to be dominated by inhomogeneous heating of the IGM at $z\sim 20$
\citep{2014MNRAS.437L..36F}, and by growing ionized bubbles during the EoR at $z\sim 7$
\todo{citation}.

@@

There are numerous ongoing efforts to detect the cosmologically redshifted 21 cm transition
including from PAPER/HERA \citep{2015ApJ...809...61A, 2016arXiv160607473D}, LOFAR
\citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B}.

\todo{discuss global experiments too}

>>>>

Studies of the cosmic microwave background (CMB) have given us an unprecedented understanding of the
universe during the epoch of recombination \citep{2013ApJS..208...19H, 2014A&A...571A..16P,
2016A&A...594A..13P}. Before arriving at the Earth, the light from the CMB propagates through the
intergalactic medium (IGM), intervening galaxies and galaxy clusters, and the Milky Way's
interstellar medium (ISM). As photons from the CMB propagate through the intervening material
scattering, absorption, or additional emission can perturb the thermal CMB spectrum. In order to
measure the pristine CMB, these foreground components (eg. synchrotron emission, free-free emission,
thermal dust emission) are a nuisance and careful modeling and removal of these components is
essential \citep{2016A&A...594A..10P, 2016A&A...594A..25P}.

However in many cases the study of CMB foregrounds is scientifically interesting in its own right.
Measurements of dust-correlated anomalous microwave emission \citep{1997ApJ...486L..23L} led to the
discovery of spinning dust emission \citep{1998ApJ...508..157D}. Thomson scattering attenuates the
CMB spectrum, but implies a mean redshift to the Epoch of Reionization (EoR) of $8.8^{+1.7}_{-1.4}$
\citep{2016A&A...594A..13P}. Inverse Compton scattering of CMB photons propagating through galaxy
clusters produces an effect known as the Sunyaev-Zel'dovich effect \citep{1970CoASP...2...66S,
1972CoASP...4..173S} that can be used to discover new galaxy clusters \citep{2010ApJ...722.1180V}
and measure the distance to galaxy clusters when combined with X-ray measurements
\citep{2006ApJ...647...25B}.

At redshifts $20 \gtrsim z \gtrsim 7$ the 21 cm hyperfine structure line of neutral hydrogen is
expected to produce a 10 to 100 mK perturbation in the CMB spectrum \citep{2006PhR...433..181F,
2012RPPh...75h6901P}. The amplitude of the perturbation on a given line-of-sight is a function of
the neutral fraction of hydrogen, the baryon overdensity, the spin temperature relative to the CMB
temperature at the given redshift, and the line-of-sight peculiar velocity of the gas.  Current 21
cm cosmology experiments can be broadly separated into two classes: global experiments that are
aiming to detect the spectral signature of the cosmologically redshifted 21 cm transition after
averaging over the entire sky, and power spectrum experiments that incorporate angular information
to attempt to measure the spatial power spectrum of cosmological 21 cm perturbations.

Ongoing global experiments include EDGES, SCI-HI, LEDA, and SARAS 2 \citep{2017arXiv170306647S}.

Ongoing power spectrum experiments include PAPER/HERA \citep{2015ApJ...809...61A,
2016arXiv160607473D}, LOFAR \citep{2017ApJ...838...65P}, and the MWA \citep{2016ApJ...833..102B}.

\todo{discuss 21cmmc ionizing efficiency, photon mean free path, minimum halo mass}
\todo{discuss what can be learned from global experiments}

The spatial power spectrum of this perturbation is expected to be dominated
by inhomogeneous heating of the IGM at $z\sim 20$ \citep{2014MNRAS.437L..36F}, and by growing
ionized bubbles during the EoR at $z\sim 7$ \todo{citation}.

@@

\todo{discuss global experiments too, edges, sci-hi, leda, saras 2}
